### 2024-03-30 tesis_Ashish/Chapter5/chapter5.tex
update 30 Mar

\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Table \refl{tab:my_labeltt}. Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing. %These variations are important to monitor as they can impact the precision of the luminosity measurement, which in turn affects the accuracy of the results obtained from the physics analyses conducted with the data.
If significant variations are observed, it may be necessary to adjust the analysis to account for these differences.

>>>>

\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Table \ref{tab:my_labeltt}. Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing. %These variations are important to monitor as they can impact the precision of the luminosity measurement, which in turn affects the accuracy of the results obtained from the physics analyses conducted with the data.
If significant variations are observed, it may be necessary to adjust the analysis to account for these differences.
